HMM Model development

### 2020-05-15 dev/hmm_model_devel.Rmd
Known initial states

data <- hmm_simulator(30, 20, 2, use_noisy_states = TRUE)

single_code <- make_stancode_hmm(data$observed_structured$formula, 
                                 serie_data = data$observed_structured$serie_data, 
                                 rate_data = data$observed_structured$rate_data, 
                                 hidden_state_data = data$observed_structured$hidden_state_data, 
                                 observed_state_data = data$observed_structured$observed_state_data,
                                 prior= data$observed_structured$prior)

@@

standata <- make_standata_hmm(data$observed_structured$formula, 
                              serie_data = data$observed_structured$serie_data, 
                              rate_data = data$observed_structured$rate_data, 
                              hidden_state_data = data$observed_structured$hidden_state_data, 
                              observed_state_data = data$observed_structured$observed_state_data,
                              sensitivity_low_bound = data$observed$sensitivity_low_bound)

@@

```{r}
noisy_states_in_sbc <- FALSE
sbc_generator <- function() {
  data <- hmm_simulator(50, 20, 3, use_noisy_states = noisy_states_in_sbc)
  standata <- make_standata_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data, sensitivity_low_bound = data$observed$sensitivity_low_bound)

>>>>

data <- hmm_simulator(5, 10, 2, use_noisy_states = TRUE)

single_code <- make_stancode_hmm(data$observed$formula, 
                                 serie_data = data$observed$serie_data, 
                                 rate_data = data$observed$rate_data, 
                                 hidden_state_data = data$observed$hidden_state_data, 
                                 initial_states = data$observed$initial_states,
                                 observed_state_data = data$observed$observed_state_data,
                                 prior= data$observed$prior)

@@

standata <- make_standata_hmm(data$observed$formula, 
                              serie_data = data$observed$serie_data, 
                              rate_data = data$observed$rate_data, 
                              hidden_state_data = data$observed$hidden_state_data, 
                              initial_states = data$observed$initial_states,
                              observed_state_data = data$observed$observed_state_data,
                              sensitivity_low_bound = data$observed$sensitivity_low_bound)

@@

```{r}
noisy_states_in_sbc <- FALSE
sbc_generator <- function() {
  data <- hmm_simulator(50, 20, 3, use_noisy_states = noisy_states_in_sbc)
  standata <- make_standata_hmm(data$observed$formula, 
                                serie_data = data$observed$serie_data, 
                                rate_data = data$observed$rate_data, 
                                hidden_state_data = data$observed$hidden_state_data, 
                                initial_states = data$observed$initial_states,
                                observed_state_data = data$observed$observed_state_data,
                                sensitivity_low_bound = data$observed$sensitivity_low_bound)
